What do incoming university students believe about open science practices in

### 2022-03-14 analysis/Manuscript.Rmd
revisions to ToP R and R

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
  - name: Jennifer L. Beaudry
    affiliation: '1,4'
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation
      - Methodology
      - Project administration
      - Validation
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    corresponding: yes
    email: jen.beaudry@flinders.edu.au
    address: Research Development and Support, Flinders University, Bedford Park, 5042
  - name: Matt N. Williams
    affiliation: '2'
    role:
      - Investigation
      - Methodology
      - Validation
      - Writing - original draft
    email: m.n.williams@massey.ac.nz
  - name: Michael C. Philipp
    affiliation: '2'
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Project administration
      - Writing - original draft
    email: m.philipp@massey.ac.nz
  - name: Emily J. Kothe
    affiliation: '3'
    role:
      - Conceptualization
      - Data curation
      - Validation
      - Visualization
      - Writing - review & editing
    email: emily.kothe@deakin.edu.au
affiliation:
  - id: '1'
    institution: Flinders University, Australia
  - id: '2'
    institution: Massey University, New Zealand
  - id: '3'
    institution: Deakin University, Australia
  - id: '4'
    institution: Swinburne University of Technology, Australia
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
acknowledgement: |
  The idea of this research was conceived at the 2018 UQ Open Science Conference and further developed at the 2019 Society for the Improvement of Psychological Science Unconference, What do first year psychology students think about (open) science?
  Our special thanks to those who contributed to the data collection effort including: Benjamin Le, Katie Gilligan-Lee, Annayah Prosser, Ian Fairholm, Jennie Ferrell, Kait Clark, Catherine Orr, Nick Burns, Rachel Searston, Rachel Stephens, Matthew Thompson, Aaron Drummond, Kathryn McGuigan, and Peter Cannon.
abstract: |
 Background: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to students’ existing understandings.
 Objective: We aimed to describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
 Method: An international online survey was conducted with participants who were about to start their first course in psychology at a university (*N* = 239).
 Results: When asked about how research should be done, most students endorsed most (but not all) of ten open science practices. When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%. Only 18% of participants had heard of the term "replication crisis".
 Conclusion: Despite relatively significant media attention on the replication crisis, few incoming psychology students in our sample were familiar with the term. The students were nevertheless sympathetic toward most open science practices, although they appeared to overestimate the prevalence of some of these practices in psychology.
 Teaching Implications: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.
keywords: open science, psychology, teaching, reproducibility, replication
wordcount: (need to update)
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
editor_options: 
  chunk_output_type: console
csl: "apa.csl" 
---

@@

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers' norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @beaudrySwinburneOpenScience2019; @harrisUseReproducibleResearch2018].

@@

# Methods
We preregistered the exploratory nature of this study at https://tinyurl.com/4p64mvwp [blinded]. Our materials, data, and analysis script are available at https://osf.io/fz6ya/?view_only=51769fc1de304ad3ba0e12a26494ac40 [blinded].

@@

Ethical approval for this study was granted by [institution blinded].

@@

Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms. <!-- Mention here our discussions workshopping of common open science norms at SIPs? JB: I think we have to, don't we?-->
The ten practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficient information of replicability, preprints, open materials, open data, and open access publishing. Although we acknowledge the merits of some of these practices are debatable [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." (see Table \@ref(tab:normcounternormitems)). Participants rated their agreement with each prescriptive statement on a 1 (*strongly disagree*) to 5 (*strongly agree*) scale. We used the scenario of a specific researcher rather than referring to psychology researchers in general in an attempt to make the questions more concrete and engaging, and because referring to a single named researcher made it easier to construct short and clear items.

@@

Participants' beliefs about the replicability of results in psychological science were indexed by two questions. The first asked participants to,

@@

Our questions focused primarily on attitudes and beliefs so that we could better document the implicit understanding that guided students’ thoughts about the research process. However, excepting the replication crisis question, we did not probe students' factual knowledge of most methodological findings or concepts. It is quite possible that reform in secondary school instruction has improved students’ understandings of more fundamental statistical (e.g., confidence interval estimation) and design (e.g., direct replications) considerations without necessarily impacting their open science attitudes and beliefs. Yet, research at the tertiary level casts doubt that the disciplinary reform from the past two decades has had much impact on the content of our teaching [@friedrichReplicatingNationalSurvey2018].

While we have interpreted our findings with respect to the norm and counternorm items as reflecting the students' personal endorsement of practices, it is plausible that their responses may have also been affected by their perceptions of what we might perceive as the "right" answers. Differences between endorsement of norms and counternorms may have also been affected by wording differences between the matched options; for example, the HARKing, information for replicability, and p-hacking counternorm items included the phrase "good scientific practice" whereas their matched norm items did not. More broadly, our choices of terminology in constructing items are very likely to have affected participants' responses to some degree. For example, the reference to keeping data "protected" in the open data counternorm item may have nudged participants towards endorsing this item, since failing to "protect" participants' data might sound irresponsible.

We did not investigate the degree to which results differed according to whether or not participants had studied psychology in high school, although interested readers could do so using our open data.

>>>>

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
  - name: Jennifer L. Beaudry
    affiliation: '1,4'
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation
      - Methodology
      - Project administration
      - Validation
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    corresponding: yes
    email: jen.beaudry@flinders.edu.au
    address: Research Development and Support, Flinders University, Bedford Park, 5042
  - name: Matt N. Williams
    affiliation: '2'
    role:
      - Investigation
      - Methodology
      - Validation
      - Writing - original draft
    email: m.n.williams@massey.ac.nz
  - name: Michael C. Philipp
    affiliation: '2'
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Project administration
      - Writing - original draft
    email: m.philipp@massey.ac.nz
  - name: Emily J. Kothe
    affiliation: '3'
    role:
      - Conceptualization
      - Data curation
      - Validation
      - Visualization
      - Writing - review & editing
    email: emily.kothe@deakin.edu.au
affiliation:
  - id: '1'
    institution: Flinders University, Australia
  - id: '2'
    institution: Massey University, New Zealand
  - id: '3'
    institution: Deakin University, Australia
  - id: '4'
    institution: Swinburne University of Technology, Australia
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
acknowledgement: |
  The idea of this research was conceived at the 2018 UQ Open Science Conference and further developed at the 2019 Society for the Improvement of Psychological Science Unconference, What do first year psychology students think about (open) science?
  Our special thanks to those who contributed to the data collection effort including: Benjamin Le, Katie Gilligan-Lee, Annayah Prosser, Ian Fairholm, Jennie Ferrell, Kait Clark, Catherine Orr, Nick Burns, Rachel Searston, Rachel Stephens, Matthew Thompson, Aaron Drummond, Kathryn McGuigan, and Peter Cannon.
abstract: |
 Background: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to students’ existing understandings.
 Objective: We aimed to describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
 Method: An international online survey was conducted with participants who were about to start their first course in psychology at a university (*N* = 239).
 Results: When asked to indicate how a researcher should conduct her study, most students endorsed most (but not all) open science practices described. When asked to estimate the proportion of published psychological studies that follow various open science practices, participants' estimates tended to average near 50%. Only 18% of participants reported that they had heard the term "replication crisis".
 Conclusion: Despite relatively significant media attention on the replication crisis, few incoming psychology students in our sample were familiar with the term. The students were nevertheless sympathetic toward most open science practices, although they appeared to overestimate the prevalence of some of these practices in psychology.
 Teaching Implications: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.
keywords: open science, psychology, teaching, reproducibility, replication
wordcount: (need to update)
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
editor_options: 
  chunk_output_type: console
csl: "apa.csl" 
---

@@

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that many close replications of published studies did not replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. Of course, psychology is not alone; the replication crisis extends to other fields, including economics [@camerer_evaluating_2016] and medicine [e.g., @errington_challenges_2021]. These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers' norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @beaudrySwinburneOpenScience2019; @harrisUseReproducibleResearch2018].

@@

# Methods
We preregistered the exploratory nature of this study at https://tinyurl.com/4p64mvwp [blinded]. Our materials, data, and analysis script are available at https://osf.io/fz6ya/?view_only=51769fc1de304ad3ba0e12a26494ac40 [blinded]. Ethical approval for this study was granted by [institution blinded].

@@

@@

Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms. The ten practices assessed in our survey are listed in Table \@ref(tab:normcounternormitems). Although we acknowledge the merits of some of these practices are debatable [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." (see Table \@ref(tab:normcounternormitems)). Participants rated their agreement separately for each norm and counternorm on a 1 (*strongly disagree*) to 5 (*strongly agree*) scale. We used the scenario of a specific researcher rather than referring to psychology researchers in general in an attempt to make the questions more concrete and engaging, and because referring to a single named researcher made it easier to construct short and clear items.

@@

Participants' beliefs about the replicability of results in psychological science were indexed by two questions. The first asked participants to:

@@

Our questions focused primarily on attitudes and beliefs so that we could better document the implicit understanding that guided students’ thoughts about the research process. However, we did not probe students' factual knowledge of most methodological findings or concepts, except the replication crisis. It is quite possible that reform in secondary school instruction has improved students’ understandings of more fundamental statistical (e.g., confidence interval estimation) and design (e.g., direct replications) considerations without necessarily influencing their open science attitudes and beliefs. Yet, research at the tertiary level casts doubt that the disciplinary reform from the past two decades has had much impact on the content of our teaching [@friedrichReplicatingNationalSurvey2018].

Although we have interpreted our findings with respect to the norm and counternorm items as reflecting  students' personal endorsement of practices, their perceptions of what we might perceive as the "right" answers could have also influenced their responses. Differences between endorsement of norms and counternorms may have also been affected by wording differences between the matched options; for example, the HARKing, information for replicability, and p-hacking counternorm items included the phrase "good scientific practice" whereas their matched norm items did not. More broadly, our choices of terminology in constructing items likely affected participants' responses to some degree. For example, the reference to keeping data "protected" in the open data counternorm item may have nudged participants towards endorsing this item, since failing to "protect" participants' data might sound irresponsible. Future research could examine the influence of revised language on participants' responses.

We did not investigate the degree to which results differed according to whether or not participants had studied psychology in high school. Interested readers could conduct this comparison using our open data.
